PM Mungbean meta-analysis

### 2021-02-03 02_Preliminary_analysis.Rmd
remove code chunk that saves Rdata file
Add inspection of crop rainfall

```{r}
save(PM_MB_dat, file = here("cache/PreliminaryData.Rdata"))
```

>>>>

### In-crop rainfall
First an inspection of all rainfall within the season
```{r season_rainfall}
source("R/add_lat_longs.R") # code adds the latitude- and longitude to PM_MB_dat
source("R/crop_rain.R")

# Obtain rainfall from bomrang
PM_MB_dat$sum_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["planting_date"],
         end = x["harvest_date"]
      )
   })

# plot yield vs rainfall
PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = sum_rain)) + 
   geom_point()
```

```{r lm_total}
summary(lm(grain_yield.t.ha. ~ sum_rain, data = PM_MB_dat))
```

```{r early_season_rain}
PM_MB_dat$early_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["planting_date"],
         end = x["first_sign_disease"]
      )
   })

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = early_rain)) + 
   geom_point()
```

```{r lm_early_rain}
summary(lm(grain_yield.t.ha. ~ early_rain, data = PM_MB_dat))
```

```{r late_rain}
PM_MB_dat$late_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = x["first_sign_disease"],
         end = x["harvest_date"]
      )
   })

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = late_rain)) + 
   geom_point()
```

```{r lm_late_rain}
summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
```

```{r mid_rain}
PM_MB_dat$mid_rain <-
   apply(PM_MB_dat, 1, function(x) {
      crop_rain(
         latitude = x["lat"],
         longitude = x["lon"],
         start = ymd(x["first_sign_disease"]) + days(30),
         end = ymd(x["first_sign_disease"]) + days(70)
      )
   })

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = mid_rain)) + 
   geom_point()
```

```{r lm_late_rain}
summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
```
